### 2021-04-01 papers/SYRCoSE/regmachine-eventstruct.tex
SYRCoSE: WIP --- reworking the text

\section{Implementation}

\subsection{How we encode Event Structures}
As we saw earlier in Step by Step Example, our event structure contains functions such as $\frf$ and $\fpred$. The events themselves are elements of some set $\mathcal{E}$ (set of identifiers), which must satisfy the following properties
\begin{definition}[identifier set]
  $\mathcal{E}$ is an identifier set if:
  \begin{itemize}
    \item There is some $ident_0 \in \mathcal{E}$ ~--- first identifier
    \item $\mathcal{E}$ has well-founded partitial order $\leqslant_\mathcal{E}$
    \item There is a function, that takes some finite $E \subset \mathcal{E}$ and returns a fresh identifier. Formally: $fresh : \mathcal{P}_{fin}(\mathcal{E}) \to \mathcal{E}$, satisfies $$\forall e \in E, \ e <_\mathcal{E} fresh(E)$$
  \end{itemize}
\end{definition}
We can fix any $\mathcal{E}$ (for example $\mathbb{N}$) and theat programm's events as a finite subset of $\mathcal{E}$

>>>>

\subsection{Event Structure of Register Machine}

In this section we present alternative operational semantics
which constructs a prime event structure encoding a 
behavior of the register machine.

The event structure is constructed incrementally 
in a step-by-step fashion by adding a single event 
on each step. In order to generate a new event 
on each step we require that events behave as \emph{identifiers}.

\begin{definition}[Identifiers set]
  We say that set $\eventSet$ together with strict partial order $\identOrd$
  form an identifier set if:
  \begin{itemize}
    \item there exist distinguished initial identifier $e_0 \in \eventSet$;
    \item there exist function $\fresh : \eventSet \fun \eventSet$ which 
      generates a new fresh identifier, \sth
      $$ \forall e \in \eventSet \ldotp e \identOrd \fresh(e) $$
  \end{itemize}
\end{definition}

Following the theory of axiomatic weak memory models~\cite{\todo{}},
we define the causality relation of the register machine's event structure
as a transitive closure of two relations~---~\emph{program order} 
and \emph{reads-from}, denoted as $\lPO$ and $\lRF$ correspondingly.

$$ \caOrd \ \defeq \ (\lPO \cup \lRF)^* $$

Program order tracks precedence of events within a single thread. 
Reads-from relation captures the flow of values from 
write events to read events, and ensures that values 
do not appear out of thin-air~\cite{\todo{}}.

In order to construct $\lPO$ and $\lRF$ incrementally
we represent them via their inverse covering functions.

\begin{definition}[Covering]
  Let $\leqslant$ be a partial order. 
  Then $lessdot$ is covering relation \wrt $\leqslant$ whenever 
  $x \lessdot y$ is true if and only if $x < y$ and 
  there is no $z$ \sth $x < z$ and $z < y$.
  A (non-deterministic) function $f : A \fun \pwset{A}$ is a covering function if
  its corresponding relation, \ie ${\frel{f} \defeq \set{\tup{x, y} ~|~ y \in f(x)}}$, 
  is a covering relation.
\end{definition}

We use the inverse covering function because it is 
more convinient in our setting. Indeed, the semanics adds new event
at each step. Then it is convinient to require that in addition 
the small-step relation is provided with the $\lPO$ and $\lRF$
predecessors of a new event.

\[\def\arraystretch{1.5}
\begin{array}{rcl|rcl}

  \lessdot_{\lPO} &\defeq& {\frel{f_{\lPO}}}^{-1}  & \lessdot_{\lRF} &\defeq& {\frel{f_{\lRF}}}^{-1} \\
  \lPO           &\defeq& \lessdot_{\lPO}^+      & \lRF           &\defeq& \lessdot_{\lRF}       \\

\end{array}
\]

The primitive conflict relation is generated by the $f_{\lPO}$ function.
The two events are considered to be in primitive conflict if they are
not equal and have a commond $\lPO$ predecessor. 
For this definition to work properly, we also need 
to assume that in the event structure each thread has 
a special initial event labeled by a distinguished 
\emph{thread start} label $\tslab{}$.

$$ e_1 \primcfRel e_2 \iff e_1 \neq e_2 \wedge f_{\lPO}(e_1) = f_{\lPO}(e2) $$

\eupp{Continue from here}

As we saw earlier in Step by Step Example, our event structure contains functions such as $\frf$ and $\fpred$. The events themselves are elements of some set $\mathcal{E}$ (set of identifiers), which must satisfy the following properties
We can fix any $\mathcal{E}$ (for example $\mathbb{N}$) and theat programm's events as a finite subset of $\mathcal{E}$
